Optimal management of a stochastically varying population when policy adjustment is costly

### 2014-06-03 manuscripts/manuscript.Rmd
ugh, error table already computed. try clean

author: 
  - name: Carl Boettiger
    affiliation: cstar
    email: 
    footnote: Corresponding author
  - name: Michael Bode
    affiliation: melbourne
  - name: James Sanchirico
    affiliation: UCD
  - name: Jacob LaRiviera
    affiliation: UTK
  - name: Alan Hastings
    affiliation: UCD
  - name: Paul Armsworth 
    affiliation: UTK

@@

```{r dependencies, include=FALSE}
source("components/install.R")
```

@@

```{r libraries, include=FALSE, cache=FALSE}
rm(list=ls())
library("rmarkdown")
library("pdgControl")
library("reshape2")
library("ggplot2")
library("data.table")
library("pander")
library("cboettigR")
library("ggthemes")
library("snowfall")
theme_set(theme_tufte())
ncpu = 1
```

@@

```{r apples_plot, dependson="quadcosts"}
#ggplot(fees, aes(c2, (npv0-value)/npv0, col=variable)) + geom_point() + geom_line()
````

@@

```{r}
v <- dt[,var(harvest), by="penalty_fn"]
var <- v$V1
names(var) <- v$penalty_fn
acor <- dt[,acf(harvest, plot=F)$acf[2], by="penalty_fn"]$V1
names(acor) <- names(var)
out <- rbind(var=var, a=acor)
```

```{r}
frac_lost <- seq(0,1, length=20)
```

@@

```{r fig4-stats}
summary_stats <- function(dt){
 harvest_var <- dt[,var(harvest), by=c("penalty_fn", "reps")]$V1
 harvest_acor <- dt[,acf(harvest, plot=F)$acf[2], by=c("penalty_fn", "reps")]$V1
 stock_var <- dt[,var(fishstock), by=c("penalty_fn", "reps")]$V1
 stock_acor <- dt[,acf(fishstock, plot=F)$acf[2], by=c("penalty_fn", "reps")]$V1
 xcor <- dt[, ccf(fishstock, harvest, plot=FALSE)$acf[2], by=c("penalty_fn", "reps")]
 setnames(xcor, "V1", "cross-correlation")

@@

```{r summary-stat-calc}
stats_summaries <- lapply(sims_at_each_apple, summary_stats)
# reformat list of data-frames as data frame with apple coef as a factor
stats_df <- melt(stats_summaries, id=names(stats_summaries[[1]]))
stats_df$L1 <- frac_lost[stats_df$L1]
names(stats_df) <- c("penalty_fn", "reps", "variable", "value", "penalty_fraction")
```

@@

```{r table-calc}
source("componetns/compute_error_table.R")
sigmas <- c(0.01, 0.1, 0.2)
reductions <- 1:3
out <- lapply(sigmas, function(s){
  lapply(reductions, function(r){
    compute_error_table(r = r, sigma = s)    
  })
})

who <- names(out[[1]][[1]])
error_df <- melt(out, id=who)              
```

```{r clean-table}
df <- error_df[2:8]
who <- c("penalty_fn", "ignore_fraction", "assume_fraction", "sigma_g", "reduction")
df2 <- melt(df, id=who)
who <- c("penalty_fn", "sigma_g", "reduction", "variable", "value")
df3 <- melt(df2, id=who)
names(df3) <- c("penalty_fn", "sigma_g", "reduction", "variable", "value", "fraction_variable", "fraction")
df3$reduction <- as.factor(df3$reduction)

#ggplot(df3) + geom_line(aes(sigma_g, value, col=reduction, lty=variable)) + facet_wrap(~penalty_fn, scales="free_y") 
```

@@

```{r Table1, results="asis", echo=FALSE}
df4 <- error_df[c(1,2,4,6,7)]
plyr::arrange(df4, penalty_fn)
pandoc.table(df4)
```

@@

      penalty fn     ignoring   assuming   percent reduction      c2
  --- ------------ ---------- ---------- ------------------- -------
    1 L1                 0.81       1.00                0.10    0.40
    2 L1                 0.62       0.99                0.20    0.81
    3 L1                 0.35       0.97                0.30    2.02
    4 L2                 0.68       0.95                0.10    0.81
    5 L2                 0.44       0.89                0.20    1.62
    6 L2                -0.28       0.81                0.30    2.83
    7 fixed              0.78       1.00                0.10    3.64
    8 fixed              0.56       0.99                0.20    8.08
    9 fixed              0.31       0.97                0.30   12.93

  Table 1: Column 'ignoring' shows the results of ignoring a adjustment penalty when it is present, Column 'assuming' shows the results of assuming an adjustment cost when it is absent. Values (ignoring, assuming) are given as the expected net present value (ENPV) as a fraction of that when no penalty is present, ENPV0.  Percent reduction refers to penalty coefficient being calibrated to achieve the given percent reduction relative to ENPV0 when the penalty is optimally accounted for.  Column c2 shows the coefficient chosen to achieve that reduction. Comparing the second and third columns shows that ignoring a real cost is a significantly graver error, particularly in the case of quadratic (L2) costs.

>>>>

author: 
  - name: Carl Boettiger
    affiliation: cstar
    email: cboettig (at) gmail.com
    footnote: Corresponding author
  - name: Michael Bode
    affiliation: melbourne
  - name: James Sanchirico
    affiliation: UCD
  - name: Jacob LaRiviera
    affiliation: UTK
  - name: Alan Hastings
    affiliation: UCD
  - name: Paul Armsworth 
    affiliation: UTK

@@

```{r dependencies, include=FALSE}
#source("components/install.R")
```

@@

```{r libraries, include=FALSE, cache=FALSE}
rm(list=ls())
library("rmarkdown")
library("pdgControl")
library("reshape2")
library("plyr")
library("ggplot2")
library("data.table")
library("pander")
library("cboettigR")
library("ggthemes")
library("snowfall")
theme_set(theme_tufte())
ncpu = 1
```

@@

@@

@@

```{r sim_at_each_apple}
frac_lost <- seq(0,1, length=20)
sims_at_each_apple <- lapply(frac_lost, fig4)
```

```{r stats-defs}
summary_stats <- function(dt){
 harvest_var <- dt[,var(harvest), by=c("penalty_fn", "reps")]$V1
 harvest_acor <- dt[,acf(harvest, plot=F)$acf[2], by=c("penalty_fn", "reps")]$V1
 stock_var <- dt[,var(fishstock), by=c("penalty_fn", "reps")]$V1
 stock_acor <- dt[,acf(fishstock, plot=F)$acf[2], by=c("penalty_fn", "reps")]$V1
 xcor <- dt[, ccf(fishstock, harvest, plot=FALSE)$acf[2], by=c("penalty_fn", "reps")]
 setnames(xcor, "V1", "cross-correlation")

@@

```{r summary-stat-calc, dependson="sim_at_each_apple"}
stats_summaries <- lapply(sims_at_each_apple, summary_stats)
# reformat list of data-frames as data frame with apple coef as a factor
stats_df <- melt(stats_summaries, id=names(stats_summaries[[1]]))
stats_df$L1 <- frac_lost[stats_df$L1]
names(stats_df) <- c("penalty_fn", "reps", "variable", "value", "penalty_fraction")
```

@@

@@

```{r table-caption}
caption = "Table 1: Column 'ignoring' shows the results of ignoring a adjustment penalty when it is present, Column 'assuming' shows the results of assuming an adjustment cost when it is absent. Values (ignoring, assuming) are given as the expected net present value (ENPV) as a fraction of that when no penalty is present, ENPV0.  Percent reduction refers to penalty coefficient being calibrated to achieve the given percent reduction relative to ENPV0 when the penalty is optimally accounted for.  Column c2 shows the coefficient chosen to achieve that reduction. Comparing the second and third columns shows that ignoring a real cost is a significantly graver error, particularly in the case of quadratic (L2) costs."
```

```{r clean-table}
who <- c("penalty_fn", "ignore_fraction", "assume_fraction", "reduction")
table1 <- arrange(subset(error_df, sigma_g == 0.01)[who], penalty_fn) 
pandoc.table(table1, caption=caption)

table1_long <- melt(table1, id = c('penalty_fn', 'reduction'))
table1_long$reduction <- as.factor(table1_long$reduction)
ggplot(table1_long, aes(penalty_fn, value, fill = variable)) + geom_bar(stat="identity", position="dodge") + facet_wrap(~ reduction) + theme_bw()
```

@@
